Review on precise spiking motifs in neurobiological and neuromorphic data

### 2022-12-25 2022-12-19_coverletter.tex
Update on Overleaf.

%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------
Many thanks for handling our manuscript entitled ``Precise spiking motifs in neurobiological and neuromorphic data'' for your consideration as a review paper in \emph{Brain Sciences}. We are very grateful to the reviewers for their very insightful remarks and we have now responded to all their remarks. Note that in agreement with the editorial office, we have added Jean-Nicolas Jérémie as an author, as his contributions were substantial during the process of writing this reviews.

@@

This is an invited Feature Paper, with a full waiver on the APC. %In addition, all the python code needed to reproduce figures and supplementary materials will be fully open-source

>>>>

%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------
Many thanks for handling our manuscript entitled ``Precise spiking motifs in neurobiological and neuromorphic data'' for your consideration as a review paper in \emph{Brain Sciences}. We are very grateful to the reviewers for their very insightful remarks and we have now responded to all their remarks.

In addition to our reports to reviewers, there is a tracked changes PDF file which highlights all changes.

\textbf{ Note that in agreement with the editorial office, we have added Jean-Nicolas Jérémie as an author, as his contributions were substantial for writing this review.}

@@

This is an invited Feature Paper, with a full waiver on the APC. In addition, all the python code needed to reproduce figures and supplementary materials will be fully open-source
